### 2014-10-29 thesis/appendix/allresults.tex
Update results tables for trauma and general data

\input{appendix/tr-corr-threshold-disc.tex}
\input{appendix/tr-corr-threshold-nodisc.tex}

\input{appendix/tr-ig-threshold-summary-disc.tex}
\input{appendix/tr-ig-threshold-summary-nodisc.tex}

\input{appendix/tr-oner-threshold-summary-disc.tex}
\input{appendix/tr-oner-threshold-summary-nodisc.tex}

\subsection{Feature Selection Results}

@@

\section{General LOS}
\subsection{Performance Results}

\subsection{Feature Selection Results}

>>>>

\input{appendix/tr-corr-threshold-summary.tex}

\input{appendix/tr-ig-threshold-summary.tex}

\input{appendix/tr-oner-threshold-summary.tex}

\clearpage
\subsection{Feature Selection Results}

@@

\clearpage
\subsection{$k$-NN Results}

\input{appendix/tr-knn-summary.tex}

\input{appendix/tr-rankeddist-summary.tex}

\clearpage
\section{General LOS}
\subsection{Performance Results}

\input{appendix/pt-all-summary.tex}

\input{appendix/pt-cfs-summary.tex}

\input{appendix/pt-wrapper-summary.tex}

\input{appendix/pt-corr-threshold-summary.tex}

\input{appendix/pt-ig-threshold-summary.tex}

\input{appendix/pt-oner-threshold-summary.tex}

\clearpage
\subsection{Feature Selection Results}

\input{appendix/pt-nothreshold-features.tex}

\input{appendix/pt-corr-threshold-features.tex}

\input{appendix/pt-ig-threshold-features.tex}

\input{appendix/pt-oner-threshold-features.tex}

\clearpage
\subsection{$k$-NN Results}

\input{appendix/pt-knn-summary.tex}

\input{appendix/pt-rankeddist-summary.tex}
